Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-15 doc/GMP2015/s08_pinnedline.tex
Changes in lemmas and proof

\item 
\todo{Trivial graphs (must be overconstrained in the original definition) does not exist??? }\
\todo{Both a single vertex and a single edge are underconstrained}
\begin{itemize}

@@

\todo{All Lemmas before Lemma 8 are proved with respect to general constraint systems,
and they go through for 2-dimensional pinned line incidence as well (without trivial graph??). }

Now we  show that Lemma 8 also holds for 2-dimensional pinned line incidence graphs.

>>>>

\item 
\todo{Over-constrained trivial subgraphs does not exist??? }\
\todo{Both a single vertex and a single edge are underconstrained}
\begin{itemize}

@@

%\todo{All Lemmas before Lemma 8 are proved with respect to general constraint systems,
%and they go through for 2-dimensional pinned line incidence as well (without trivial graph??). }
Lemmas similar to Lemma 2--5 hold for 2-dimensional pinned line incidence graphs.

\begin{lemma}
Let $F_j$ and $F_j$ be well-constrained subgraphs of the same well-constrained graph $F$. 
 $F_i \cup F_j$ can only be well-constrained.
\end{lemma}

\begin{proof}
\begin{enumerate}
\item Obviously $F_i \cup F_j$ cannot be over-constrained since it is a subgraph of well-constrained graph $F$.
\item $F_i \cup F_j$ cannot be under-constrained, otherwise $F_i \cap F_j$ would be over-constrained while there are no trivial over-constrained graphs. 
\item The only remaining case is that $F_i \cup F_j$ is well-constrained, which is true if and only if $F_i \cap F_j$ is well-constrained.
\end{enumerate}
\end{proof}

Lemma 6 and 7 straightforwardly holds for 2-dimensional pinned line incidence graphs. 
Now we  show that Lemma 8 also holds.
